Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-01 AAMAS2021/minimax.tex
my abstract proposition

\begin{abstract}
Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided. However, requiring the agents to express full preference orderings can be costly, and formalizing a voting rule it is not an easy task. Methods for eliciting the voting rule when the preferences of the agents are completely known have been proposed, as well as techniques that consider the opposite scenario.
However, both of them may be unknown.
This paper addresses this case, and proposes a method which permits to obtain recommendations without requiring full knowledge of either.
Focusing on positional scoring rules, we assume that the chair, while  not able to give a precise definition of the rule, is capable of answering simple questions  requiring to pick a winner from a specific  example profile. Moreover, the preferences of the agents are incrementally acquired by asking comparison queries.
In this setting, we propose a method  for robust approximate winner determination with minimax regret. We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that interleave questions to the chair and questions to the agents in order to attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative. 
\end{abstract}

>>>>

\begin{abstract}
Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters). In the classical setting, the voting rule is fixed beforehand and full information regarding the preferences of the agents is provided. In practice, this is not always the case. Requiring the agents to express full preference orderings can be costly, and formalizing a voting rule is not an easy task for non-expert users. Methods for eliciting the voting rule when the preferences of the agents are completely known have been proposed, as well as techniques that consider the opposite scenario. However, there may be cases where both of them are only partially known.
This paper considers both sources of uncertainty at the same time, and proposes a method able to recommend a consensus choice without requiring full knowledge of either.
Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a specific example profile. In addition, the preferences of the agents are incrementally acquired by asking comparison queries. 
In this setting, we propose a method for robust approximate winner determination with minimax regret. We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies which attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative.
\end{abstract}
